---
title: "Lab 00 - Hello IDS!"
author: "Aksel Huillard d'Aignaux"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Nereus", "Leonardo", "Ben", 
           "Aksel"),
  github_username = c("Nereus", "Leonardo", "Ben", 
                      "Aksel010"), 
  colour = c("powderblue", "green", "black", 
             "orange"),
  hobby = c("Football", "Rugby", "Swimming", 
            "Drinking"),
  favourite_number = c(2, 7, 4, 3)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The plot shows who has the largest favourite number on the team.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "GitHub Username", 
          y = "favourite number",
          title = "Who has the largest favourite number?")
```

I think labs command dictates the labels on axis and title of the project.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

Because if there is a really broad range of hobbies, it will be similar to the graph we already have but on a larger scale, not revealing much information on the data. Instead, you could use a pie chart. You could also even group the data into categories such as sport, Arts etc.
